\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{titling}
\usepackage{url}
\usepackage{array}
\usepackage{enumerate}
\usepackage{ physics }
\usepackage[hmargin=3.5cm,vmargin=2.5cm]{geometry}
\title{Smartphone Spectrophotometer Notes}
\author{Shehtab Zaman }
\date{December 2017}

\begin{document}
\maketitle
\section{Introduction}

\subsection{Outline of Procedure}
The problem of using variable smartphone cameras for the
spectrophotometry of lake water consists of a set of challenges.
The general outline of the procedure is as follows:
\begin{enumerate}
\item Obtain the raw image data for submerged and unsubmerged secchi disk
\item Obtain the intensities of the captured image using QE Curves
\item Normalize intensity to baseline factoring in shutter speed and aperture
\item Obtain intensity of a particular wavelenth provided RGB value
\item From Beer-Lambert law find the concentration of materials in the water
\end{enumerate}

% \section{Background}
\section{Sensor Baseline}

\subsection{Compensating for Exposure}

\subsubsection{Aperture and Intensity}

The aperture of, measured in f-stops, is the opening of the camera sensor. the
f-stop measures the amount of sensors surface open to collect photons. Larger
apertures create a smaller depth of field (should be considered when deciding on the baseline).

The intensity of the incident light is inversely proportional to the square of the
f-number.
$$ I \propto \frac{1}{f^2} $$

\subsubsection{Shutter Speed and Intensity}
We can assume that the shutter speed (how long the sensor collects photons), is inversely proportional
to the measured intensity.

$$ I \propto \frac{1}{T}$$

\subsubsection{Pixel values}

If the pixel value is an estimate of the power per solid angle per area of the sensor, we can combine the
shutter speed and aperture relations as

$$ I \propto \frac{1}{T \cdot f^2}$$
%\section{Ambient Light Baseline}
\section{Wavelength Intensity}

The raw data obtained from the camera provides us with the three values in the
R,G,B channels per pixel (see mathemtica for example). Given a specific wavelength, $ \lambda$, we want to obtain the
\underline{intensity} at that wavelenth.

\subsection{Spectral Sensitivity Function}

Given constant ISO and aperture, at each wavelenth, $ \lambda$, the spectral sensitivity
in RGB channels is calculated by
$$ c(\lambda) = \frac{d(\lambda)}{r(\lambda) t(\lambda)} $$
where, $ r(\lambda)$ is the radiance. $t(\lambda) $ is the exposure time.
$d(\lambda)$ is the data.

Therefore rdiance at a wavelength would be,

$$ r(\lambda) = \frac{d(\lambda)}{c(\lambda)t'(\lambda, f)} $$

with $t'(\lambda) $ is a function of the wavelength and aperture as well.

\section{Absorbance Model}
\subsection{Lambertian BRDF}
\subsubsection{Unsubmerged Secchi Disk Model}

Assuming a diffuse reflection and rotational symmetry of the
secchi disk, we can assume the Lambertian BRDF to be
as constant, with the form,
\[
f(\theta_i, \phi_i; \theta_r , \phi_r) = \frac{\rho_d}{\pi}
\]

The $\rho_d$ is the albedo of the secchi disk.

Inside the water column with the assumption that the light source is normal to the surface,
the surface radiance is then,

\[
L = \frac{\rho_d}{\pi} I_0
\]

Where, $I_0$ is the intensity of the incident light.

\subsubsection{Intensity as }

% \underline{Note:} The intensity of light in the water will lower than
% the intensity of light outside. The refractive be taken into account in the
% rendering equation.
% (The incident light will need to take into account Fresnel Diffraction possibly?)

\section{References}

\begin{thebibliography}{9}
  \bibitem{test}
\end{thebibliography}



\end{document}
